---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples. 

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`). 

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165

### Read in the data 

There are no problems here. 
```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 1: 
# I closed the parenthesis around (is.character), tolower

mack_creek_lengths <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>% 
  mutate(across(where(is.character), tolower)) %>% 
  drop_na(species) %>% 
  group_by(species) %>% 
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()
```

### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
# I put color = "purple" inside parenthesis and then took shape = 12 and put it outside the parenthesis 

mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% 
  ggplot(aes(x = length1, y = weight)) +
         geom_point(color = "purple", shape = 12) +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
```

## End


# First reprex 
```{r}
library(reprex)

data_frame <- tribble(
  ~name, ~weight, ~hair_color,
  "Magoo", 65, "Tan and white",
  "Arthur", 60, "Tan and white",
  "Zennie", 75, "Tri color"
)

data_frame %>%
  ggplot(aes(x = name, y = weight)) +
         geom_point(color = "purple", shape = 12)

# I found out that in geom_point, having aesthetics contain color = "purple" does not work because shape is not a variable in my data frame. 
  
```
# Second reprex 
```{r}
library(reprex)

data_frame <- tribble(
  ~Name, ~Weight, ~Hair_Color,
  "Magoo", 65, "Tan and White",
  "Arthur", 60, "Tan and White",
  "Zennie", 75, "Tri Color"
)

new_data_frame <- data_frame %>%
  mutate(across(where(is.character), tolower))

new_data_frame
# I discovered that my code was not running correctly because I did not put parenthesis around `(is.character)` with `, tolower` inside of the second parenthesis. This makes all of my observation values lowercase. 

```
















